---
output: html_document
editor_options: 
  chunk_output_type: inline
---
---

Exercício2
```{r}
dados2 = read.csv("tempo.csv",sep = ";", na.strings="", stringsAsFactors=T)
head(dados2)
```


```{r}
summary(dados2)
```
```{r}
counts = table(dados2$Aparencia)
barplot(counts, main="Aparencia", xlab="Aparencia")
```
```{r}
unique(dados2$Aparencia)
```


```
```{r}
# Aparencia
summary(dados2$Aparencia)
boxplot(dados2$Aparencia)
hist(dados2$Aparencia)
```
```{r}
# Temperatura
summary(dados2$Temperatura)
boxplot(dados2$Temperatura)
hist(dados2$Temperatura)
```
```{r}
# Umidade
summary(dados2$Umidade)
boxplot(dados2$Umidade)
hist(dados2$Umidade)

```
```{r}
# Vento
summary(dados2$Vento)
boxplot(dados2$Vento)
hist(dados2$Vento)
```


```{r}
# Jogar
summary(dados2$Jogar)
boxplot(dados2$Jogar)
hist(dados2$Jogar)
```

```{r}
summary(dados2$Id)
dados2[!complete.cases(dados2),]
summary(dados$Umidade)
median(dados2$Umidade, na.rm=T)
dados2[is.na(dados2$Umidade) ,]$Umidade = median(dados2$Umidade, na.rm=T)
summary(dados$Umidade)
dados2[!complete.cases(dados2$Umidade),]
```


```{r}
dados2 = dados2[-c(4),]
```


```{r}
dados2 = read.csv("tempo.csv",sep = ";", na.strings="", stringsAsFactors=T)
head(dados2)
```
```{r}
unique(dados2$Umidade)
dados2$Umidade = factor(dados2$Umidade)
unique(dados2$Umidade)
```
```{r}
dados2 = read.csv("tempo.csv",sep = ";", na.strings="", stringsAsFactors=T)
head(dados2)
```
```{r}
boxplot(dados2$Umidade)
boxplot(dados2$Umidade, outline= F)
x = boxplot(dados2$Umidade)$out
x
dados2 = dados2[-c(4),]
```
```{r}
dados2 = read.csv("tempo.csv",sep = ";", na.strings="", stringsAsFactors=T)
head(dados2)
```
```{r}
dados2$Umidade = factor(dados2$Umidade(Id=4))
rownames(dados2)
dodos3 = dados2[(-4),]

